---
title: "Alcohol vs Seat choice"
author: "Sisilia Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Looking at the box plot you can infer that the back row consumes more alcohol than the first and middle rows.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The people in the back row have a mean more than 3x higher than the mean for the people in the front and middle row.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

since the p value from one way anova was such a small number we are going to follow up with TurkeyHSD

```{r}
plot(TukeyHSD(model1))
```

Looking at the comparison chart, the front and back row you can see a major difference between the two since it lands all below zero. Just like the front and bacl row, the middle and back row comparison also has a major difference which is why it shows the line below zero as well. However when you compare the middle and front row you can see that there is not a major difference since the line does it zero and includes positive confidence integers.

## Conclusions


